\TheTitle

### 2017-07-13 paper/study.tex
Minor cleanup on user opinions
This section is small, just fixing some typos and wording.

Among the 12 pariticipants, there was nearly unanimous agreement that
for conceptual understanding and summarization tasks, \tool was easier
to work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git commandline may be to
extract the a good conceptual understanding from the DAG, and perform
the summarization tasks from the commandline. One of these three
participants said that they would prefer to have both tools available,
as they are able to complement each other.

>>>>

Among the 12 participants, there was nearly unanimous agreement that
for conceptual understanding and summarization tasks, \tool was easier
to work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git command-line may be to
extract a conceptual understanding from the DAG and perform the
summarization tasks. One of these three participants said that they
would prefer to have both tools available, as they are able to
complement each other.
